Capon Beamforming Applied on Moving Objects - An Analysis of Local Shift-Invariance

### 2013-10-27 HRUIofMovingObjects/jrnl_article.tex
Moving objects paper: done some writing 2.0.

\newcommand\multimedia[1]{\textbf{{\color{red}#1}}}
\newcommand\comment[1]{\textit{{\color{red}#1}}}

@@

\section{Local Shift Invariance of the Capon Beamformer}
Now we will investigate the lateral local shift-invariance of the Capon beamformer with typical parameters. A

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2.eps}\label{fig:capon}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=1_2.eps}
}
}
\caption{...}
\label{fig:image_capon}
\end{figure*}

>>>>

\newcommand\multimedia[1]{\textbf{{\color{red}#1}}}
\newcommand\comment[1]{\textit{{\color{red}(#1)}}}

@@

\section{Local Shift Invariance of the Capon Beamformer}
We will now investigate the lateral local shift-invariance of the Capon beamformer with parameters equal to the once used in earlier work \comment{cite}. A  . Fig.\,\ref{fig:capon1}.

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2.eps}\label{fig:capon1}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=1_2.eps}\label{fig:capon2}
}
}
\caption{...}
\label{fig:image_capon}
\end{figure*}
